### 2018-11-07 Sections/collision_handling_and_classical_errors.tex
Indexing up to N
Restructured microwaves

\subsection{Collision handling \& classical errors} \label{sec:collision} \index{Collision handling} \index{Classical errors}

@@

As discussed, quantum collision detection is complicated by the fact that measuring quantum data to determine whether it has been corrupted disturbs the quantum state. We address this problem by taking advantage of the duality of the quantum/classical network, discussed in Sec.~\ref{sec:quant_net}. Because the quantum and classical components of the \textsc{Packets} are synchronised and of equal length (thanks to the \textsc{Padding} field of the \textsc{Packet Header}), and because the same applies to all other \textsc{Packets} on the network, a collision in the quantum data necessarily implies a collision in the classical data, and vice versa. Therefore, by applying regular classical collision detection techniques based on checksums (recall \textsc{Packet Header} contains a \textsc{Checksum} field), we can infer collisions in quantum data without actually measuring it. We refer to this as \textit{indirect collision detection}\index{Indirect collision detection}. This guarantees us the ability to detect when a collision has occurred, in which case both quantum \textit{and} classical data are corrupted, or has not occurred, in which case both quantum and classical data are uncorrupted and the quantum data remains unmeasured. Collision detection is incorporated into the pseudo-code implementation of the \textsc{Transport} layer shown in Alg.~\ref{alg:transport_alg}.

>>>>

\subsection{Collision handling \& classical errors} \label{sec:collision} \index{Collisions!Handling} \index{Classical errors}

@@

As discussed, quantum collision detection is complicated by the fact that measuring quantum data to determine whether it has been corrupted disturbs the quantum state. We address this problem by taking advantage of the duality of the quantum/classical network, discussed in Part \ref{part:quant_net}. Because the quantum and classical components of the \textsc{Packets} are synchronised and of equal length (thanks to the \textsc{Padding} field of the \textsc{Packet Header}), and because the same applies to all other \textsc{Packets} on the network, a collision in the quantum data necessarily implies a collision in the classical data, and vice versa. Therefore, by applying regular classical collision detection techniques based on checksums (recall \textsc{Packet Header} contains a \textsc{Checksum} field), we can infer collisions in quantum data without actually measuring it. We refer to this as \textit{indirect collision detection}\index{Indirect collision detection}. This guarantees us the ability to detect when a collision has occurred, in which case both quantum \textit{and} classical data are corrupted, or has not occurred, in which case both quantum and classical data are uncorrupted and the quantum data remains unmeasured. Collision detection is incorporated into the pseudo-code implementation of the \textsc{Transport} layer shown in Alg.~\ref{alg:transport_alg}.

### 2018-11-07 Sections/entanglement_the_ultimate_quantum_resource.tex
Restructured microwaves

Given this plethora of protocols and encodings, discussed in detail in Sec.~\ref{sec:protocols_quant_int}, one might ask whether there is a single primitive resource that might be applicable to all, or at least most of these quantum protocols, thereby reducing the technological requirements of the nodes and quantum channels forming the network mediating them -- if networks were able to specialise in a very limited number of tasks, we might reasonably expect them to be better optimised and exhibit better performance than a `Jack of all trades' network!

>>>>

Given this plethora of protocols and encodings, discussed in detail in Part \ref{part:protocols}, one might ask whether there is a single primitive resource that might be applicable to all, or at least most of these quantum protocols, thereby reducing the technological requirements of the nodes and quantum channels forming the network mediating them -- if networks were able to specialise in a very limited number of tasks, we might reasonably expect them to be better optimised and exhibit better performance than a `Jack of all trades, master of none' network!

### 2018-11-07 Sections/essay_to_the_future_QKD.tex
Restructured microwaves

The RR-DPS protocol \cite{bib:sasaki2014practical} removes the need to monitor signal disturbance. In a conventional QKD protocol, the noise parameter needs to be estimated; and if high precision is required, the portion of the signal that is sacrificed increases, thus decreasing the efficiency of the protocol \cite{bib:cai2009finite, bib:hayashi2014security}. This protocol has a high tolerance to the qubit error rate ($< 50\%$) \cite{bib:xu2015discrete}, and makes it attractive for implementation when high systematic errors are unavoidable.

>>>>

The RR-DPS protocol \cite{bib:sasaki2014practical} removes the need to monitor signal disturbance. In a conventional QKD protocol, the noise parameter needs to be estimated; and if high precision is required, the portion of the signal that is sacrificed increases, thus decreasing the efficiency of the protocol \cite{bib:cai2009finite, bib:hayashi2014security}. This protocol has a high tolerance to the qubit error rate ($<50\%$) \cite{bib:xu2015discrete}, and makes it attractive for implementation when high systematic errors are unavoidable.

### 2018-11-07 Sections/interconnecting_and_interfacing_quantum_networks.tex
Finished indexing hierarchy
Restructured microwaves

\subsubsection{Two-level systems} \index{Two-level systems}

@@

%
% Microwave Qubits
%

\subsubsection{Microwave qubits}

\comment{To do. Jon Dowling.}

>>>>

\subsubsection{Two-level systems} \index{2-level systems}

@@

%
% Superconducting Qubits
%

\subsubsection{Superconducting qubits}\index{Superconducting qubits}\index{Quantum transducers}\index{Microwave qubits}

In the context of superconducting qubits (Sec.~\ref{sec:artificial_atoms}), the energy difference between the energy levels being utilised to encode the qubit is extremely small. Therefore photons coupled to these transitions sit in the microwave regime, whose wavelength lies in the range \mbox{$\lambda\sim100\mu$m-1m}.

%To build a scalable quantum computer, multiple qubits are required, with the ability to interact with one another. Hence, it is essential to find ways to transfer quantum information between distinct superconducting qubits. When doing so, it is essential that quantum coherence be preserved. This implies we need to find a different kind of qubit, which can carry information from one place to another, but interacts only weakly with the other qubits and the environment. Photons are the ideal candidate for this (Sec.~\ref{sec:opt_enc_of_qi}). Photonic qubits for carrying information should have frequencies equal to the energy difference between qubit levels. For a superconducting qubit, the energy difference is very small, hence the frequency of optical qubits is in microwave regime, .

Information transfer between distinct superconducting qubits is achieved using a resonator, which acts as a quantum data bus\index{Quantum data bus}. A simple resonator\index{Resonators} is an LC circuit\index{LC circuit}, which can support only one frequency mode, but a waveguide resonator can support multiple modes. In general, the transmission line circuits used in non-linear quantum electric circuits\index{Non-linear quantum electric circuits} are in the form of coplanar waveguides\index{Waveguides}. These waveguides are engineered to handle a particular set of frequencies, and produce transmission lines with tuneable frequency. Tuneable resonators\index{Tuneable resonators} are very important in quantum optics, and are useful in implementing controllable coupling between different quantum elements, and also in shaping photon wave-packets.

In cavity quantum electrodynamics (QED)\index{Quantum electrodynamics} the interaction of a natural atom with an optical photon in the visible wavelength regime is considered. Similarly, the interaction between quantum non-linear electrical circuits and  microwave photons are investigated in circuit QED. The coupling-strength between a natural atom and visible light photon is fixed, where atoms couple weakly with photons \cite{bib:raimond2001manipulating}. Meanwhile, the coupling-strength between a superconducting qubit and a microwave can be manipulated by engineering the parameters of the qubit and resonator, yielding strong and ultra-strong coupling\index{Strong coupling}\index{Ultra-strong coupling} between qubits and photons \cite{bib:wallraff2004strong} (see Fig.~\ref{fig:microwave_qubits}). Furthermore, the coupling between an atom and a photon can be tuned dynamically during the course of an experiment. Several quantum optics components such as mirrors, beamsplitters, circulators and switches can also be designed based on quantum electric circuits.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{microwave_qubits}
\caption{Schematic sketch of the interaction between superconducting qubits and microwave qubits. The superconducting qubits are in the entangled state \mbox{$\frac{1}{\sqrt{2}}(\ket{e,g} + \ket{g,e})$}, where $\ket{g}$ and $\ket{e}$ are the ground and excited states of the superconducting qubits. These are subjected to interact with the flying qubits, the microwave qubit (red dashed arrow). The photons become entangled and the output state of the photons are \mbox{$\frac{1}{\sqrt{2}}(\ket{H,V} + \ket{V,H})$}, where $\ket{H}$ and $\ket{V}$ are the horizontal and vertical polarisation modes respectively.}\label{fig:microwave_qubits}\index{Microwave qubits}
\end{figure}

%\subsubsection{Quantum transducers}

Due to scalability requirements, superconducting qubits are the most widely used qubit implementation used today. The energy-level spacing in superconducting qubits lie in the microwave regime. Hence to control and transfer information from a superconducting qubit one might need to use microwave photons. In principle, we can use microwave photons to transfer information from one node to another, but such a transmission process is extremely lossy. Also, such processes have very demanding technical requirements, like the design of specialised Niobium waveguides\index{Niobium waveguides}, maintained at extremely low temperatures. Hence it isn't feasible to use microwave photons for the long-distance transfer of quantum information. Meanwhile, it is well known that photons in the visible spectrum can be transmitted easily using optical fibres, with favourable efficiency.

To convert microwave photons to optical photons we can use a quantum transducer. A sketch of a typical design for a quantum transducer\index{Quantum transducers} is shown in Fig.~\ref{fig:quantum_transducer} through a flowchart diagram. The quantum computer is made up of superconducting qubits, which feed quantum information to microwave qubits. The microwave qubits are then interfaced to optical qubits in the visible spectrum through a 3-level quantum system\index{3-level systems}, which can couple at both microwave and optical frequencies. These steps should be reversible. Hence it should be possible to convert the optical qubits back into microwave qubits at the receiving end.

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=\textwidth]{quantum_transducer}
\else
\includegraphics[clip=true, width=0.475\textwidth]{quantum_transducer}
\fi
\caption{Block diagram for the quantum transducer. The quantum computer comprising superconducting qubits couples with the microwave qubit. The microwave qubit and the photonic qubit are coupled by a three-level system in which the energy difference between the levels correspond to both microwave and visible optical frequencies. The thick arrows denote the forward process, required to convert the microwave to optical frequencies, and the dashed arrows represent the reverse process, required at the receiving end to convert the optical frequency to a microwave frequency.}\label{fig:quantum_transducer}
\end{figure}

There are several proposals for quantum transducers in existence and they can be classified into two major classes:
\begin{itemize}
	\item Opto-mechanical \cite{bib:rabl2010quantum, bib:barzanjeh2011entangling, bib:bochmann2013nanomechanical, bib:didier2014quantum, bib:schuetz2015universal, bib:shumeiko2016quantum, bib:stannigel2010optomechanical}.
	\item Spin-ensembles \cite{bib:imamouglu2009cavity, bib:blum2015interfacing}.
\end{itemize}

The opto-mechanical quantum transducer\index{Opto-mechanical quantum transducer} (see Fig.~\ref{fig:opto_mechanics_transducer}), as the name suggests, combines optical components with a nano-mechanical resonator and converts the microwave photon\index{Phonons} into a phonon (acoustic) mode. The acoustic mode is then transmitted via waveguides\index{Waveguides}. Since we need to fabricate waveguides with very high precision to transmit phonon modes, this scheme is not suitable for communicating between two distant quantum computers. A coupling of the phonon mode to the optical photon mode in the visible region was suggested to enable long-distance transfer of quantum information.

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=\textwidth]{transducer_scheme_1}
\else
\includegraphics[clip=true, width=0.475\textwidth]{transducer_scheme_1}
\fi
\caption{Scheme for an opto-mechanics-based quantum transducer. There are two possible ways of converting microwaves. The final steps for the process in which acoustic modes are transported using waveguides is enclosed by a brown coloured box with dashed outlines labeled (a). Similarly the blue coloured box labeled (b) represents the scheme where phonons are converted to optical photons which are then transmitted via optical fibres. The initial few steps consisting of the superconducting qubit, transmission line resonator and microwaves are common to both processes.}\label{fig:opto_mechanics_transducer}\index{Opto-mechanical quantum transducer}
\end{figure}

The Hamiltonian of an opto-mechanical quantum transducer, which converts a microwave photon to optical photon using an intermediate nano-mechanical resonator\index{Nano-mechanical resonator} reads,
\begin{align}
\hat{H} &= \hbar \omega_{1} \, \hat{a}_{1}^{\dag} \hat{a}_{1} + \hbar \omega_{2} \, \hat{a}_{2}^{\dag} \hat{a}_{2} \nonumber\\
&+ \hbar \Omega \, \hat{b}^{\dag} \hat{b} + \hbar \, g \, (\hat{b}+\hat{b}^{\dag}) (\hat{a}_{2}^{\dag} \hat{a}_{1} + \hat{a}_{1}^{\dag} \hat{a}_{2}),
\end{align}
where $\omega_{1}$ ($\omega_{2}$) is the frequency of the microwave (optical) photon, and $\Omega$ is phonon frequency. The operators $\hat{a}_{1}$ ($\hat{a}_{1}^{\dag}$) and $\hat{a}_{2}$ ($\hat{a}_{2}^{\dag}$) denote the annihilation (creation) operators corresponding to the microwave and optical photons respectively. Meanwhile, $\hat{b}^{\dag}$ ($\hat{b}$) denotes the phonon creation (annihilation) operator corresponding to the phonons. The factor $g$ is the coupling-strength between the microwave, phonon and photon modes. This design for a quantum transducer is widely preferred, since the optical photons in the visible spectrum can be transmitted over long distances using fibre optics. But the scheme requires two intermediate conversions, each of which reduces overall efficiency.

The spin-ensemble-based quantum transducer\index{Spin-ensemble quantum transducer} (see Fig.~\ref{fig:spin_ens_transducer}) is an alternative to the opto-mechanical quantum transducer. In this scheme an ensemble of spins interact with microwave qubits via magnetic dipole coupling\index{Magnetic dipole coupling}, while the superconducting qubits interact via electric dipole coupling\index{Electric dipole coupling} with the microwave coupling. The Hamiltonian for such a system is,
\begin{align}
\hat{H} = \hat{H}_{\mathrm{mw}} + \hat{H}_{\mathrm{spin}} + \hat{H}_{\mathrm{opt}},
\end{align}
where,
\begin{align}
\hat{H}_{\mathrm{mw}} &= \hbar \omega_\mathrm{sq} \hat\sigma_\mathrm{sq}^{\dag} \hat\sigma_\mathrm{sq} + \hbar \omega_{\mu} \hat{a}^{\dag} \hat{a} + \hbar g_{\mu} (\hat{a}^{\dag} \hat\sigma_\mathrm{sq} + \hat{a} \hat\sigma_\mathrm{sq}^{\dag}),\nonumber \\
\hat{H}_{\mathrm{spin}} &= \hbar g_\mathrm{s} (\hat\sigma_\mathrm{ba}^{\dag} \hat\sigma_\mathrm{ba} + \hat\sigma_\mathrm{bs}^{\dag} \hat\sigma_\mathrm{bs}), \nonumber\\
\hat{H}_{\mathrm{opt}} &= \hbar g_\mathrm{ab} (\hat\sigma_\mathrm{ba}^{\dag} \hat{c} + \hat{c}^{\dag} \hat\sigma_\mathrm{ba}).
\end{align}

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.9\textwidth]{transducer_scheme_2}
\else
\includegraphics[clip=true, width=0.475\textwidth]{transducer_scheme_2}
\fi
\caption{The spin-ensemble-based quantum transducer. Microwave photons are converted to optical photons via a spin-ensemble.}\label{fig:spin_ens_transducer}\index{Spin-ensemble quantum transducer}
\end{figure}

The factor $\omega_\mathrm{sq}$ is the frequency of the superconducting qubit, and $\hat\sigma_\mathrm{sq}^{\dag}$ and $\hat\sigma_\mathrm{sq}$ are the raising and lowering operators\index{Raising operators}\index{Lowering operators} corresponding to the superconducting qubits. The frequency of the microwaves is given by $\omega_{\mu}$, and the $\hat{a}^{\dag}$ and $\hat{a}$ are the creation and annihilation operators for the microwave photons. The factor $g_{s}$ is the coupling strength between the various levels of the spin, and $\hat\sigma_\mathrm{ba}$ and $\hat\sigma_\mathrm{bs}$ are the spin operators corresponding to the transition between the level $a$, $b$ and $s$. Finally, the coupling strength of the spin interaction with the photon is denoted by $g_\mathrm{ab}$, and $\hat{c}^{\dag}$ ($\hat{c}$) is the creation (annihilation) operator corresponding for the photon. Again this is a two-step process, which is in addition beset with the problem of inhomogenous line broadening\index{Inhomogenous line broadening}. The design of an experimental, high-fidelity quantum transducer is still an open and ongoing challenge in the field of quantum technology.

### 2018-11-07 Sections/network_topologies.tex
Restructured microwaves

Let the graph $G$ representing the network be,
\begin{align}
G=(V,E),	
\end{align}
with vertices $V$ and edges $E$. In principle a network could be characterised by any connected graph whatsoever. However, there are certain structures and patterns that emerge very frequently and deserve special attention.

@@

@@

\begin{figure}[!htbp]
\includegraphics[clip=true,width=0.4\textwidth]{scale_free_network}
\caption{Example of a scale-free network. The graph exhibits a highly hierarchical structure, with a small number of `hub' nodes that are highly connected (green, with vertex order 5), that connect downward to a larger number of less connected nodes (purple, with order vertex 1-2).}\label{fig:scale_free_net}
\end{figure}

>>>>

Let the graph $G$ representing the network be,
\begin{align}\index{Graphs}
G=(V,E),	
\end{align}
with vertices $V$ and edges $E$. In principle a network could be characterised by any connected graph whatsoever. However, there are certain structures and patterns that emerge very frequently and deserve special attention.

@@

In general, the MST of a graph is not unique, and there may be an arbitrarily large number of completely differently structured MSTs all with the same minimum weight.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true,width=0.4\textwidth]{scale_free_network}
\caption{Example of a scale-free network. The graph exhibits a highly hierarchical structure, with a small number of `hub' nodes that are highly connected (green, with vertex order 5), that connect downward to a larger number of less connected nodes (purple, with vertex order 1-2).}\label{fig:scale_free_net}
\end{figure}

### 2018-11-07 Sections/optical_encoding_of_quantum_information.tex
Restructured microwaves

A very attractive feature of single photons is that they undergo very little decoherence, even over large distances -- dephasing (Sec.~\ref{sec:dephasing_error}) in the polarisation degree of freedom, for example, is negligible in free-space. They are, however, very susceptible to loss, and protocols relying on many single-photon states suffer exponential decay in their success rates as the number of photons is increased (Sec.~\ref{sec:eff_err}).

We can encode a single qubit into a single photon in the polarisation basis using the horizontal and vertical polarisation degrees of freedom. Equivalently, one can employ `dual rail' encoding, whereby a single photon is placed into a superposition across two spatial modes. Finally, one can use time-bin encoding, whereby discrete windows of time represent logical basis states when occupied by a photon. This leads to the equivalent representations for logical qubits ($L$),
\begin{align} \label{eq:single_photon_enc}\index{Polarisation encoding} \index{Dual-rail encoding}
\ket{\psi}_\mathrm{qubit} &\equiv \alpha\ket{0}_L + \beta\ket{1}_L, \nonumber \\
\ket{\psi}_\mathrm{pol} &\equiv \alpha\ket{H} + \beta\ket{V}, \nonumber \\
\ket{\psi}_\mathrm{dual} &\equiv \alpha\ket{0,1} + \beta\ket{1,0}, \nonumber \\
\ket{\psi}_\mathrm{temporal} &\equiv \alpha\ket{0_t,1_{t+\tau}} + \beta\ket{1_t,0_{t+\tau}},
\end{align}
shown graphically in Fig.~\ref{fig:photonic_qubit_encodings}.

@@

Completely independent of the photon-number degree of freedom, are the spatio-temporal degrees of freedom, which encode the spatial, temporal, or spectral structure of photons. In the temporal domain, for example, we could define the temporal structure of a single photon as,
\begin{align}
\ket\psi_\mathrm{temporal} = \int_{-\infty}^\infty \psi(t) \hat{a}^\dag(t)\,dt\,\ket{0},
\end{align}
where $\hat{a}^\dag(t)$ is the time-specific photonic creation operator, and $\psi(t)$ is the temporal distribution function \cite{bib:RohdeFreqTemp05}.

@@

The TEM modes are discrete, and denoted TEM$_{mn}$, where \mbox{$m,n\in \mathbb{Z}_+$}. TEM modes can be prepared and manipulated using holograms\index{Holograms} in the form of phase-masks.

>>>>

A very attractive feature of single photons is that they undergo very little decoherence, even over large distances -- dephasing (Sec.~\ref{sec:dephasing_error}\index{Dephasing}) in the polarisation degree of freedom, for example, is negligible in free-space. They are, however, very susceptible to loss, and protocols relying on many single-photon states suffer exponential decay in their success rates as the number of photons is increased (Sec.~\ref{sec:eff_err}).

We can encode a single qubit into a single photon in the polarisation basis using the horizontal and vertical polarisation degrees of freedom. Equivalently, one can employ `dual rail' encoding, whereby a single photon is placed into a superposition across two spatial modes. Finally, one can use time-bin encoding, whereby discrete windows of time represent logical basis states when occupied by a photon. This leads to the equivalent representations for logical qubits ($L$),
\begin{align} \label{eq:single_photon_enc}\index{Polarisation encoding} \index{Dual-rail encoding}
	\index{Time-bin encoding}
\ket{\psi}_\mathrm{qubit} &\equiv \alpha\ket{0}_L + \beta\ket{1}_L, \nonumber \\
\ket{\psi}_\mathrm{pol} &\equiv \alpha\ket{H} + \beta\ket{V}, \nonumber \\
\ket{\psi}_\mathrm{dual} &\equiv \alpha\ket{0,1} + \beta\ket{1,0}, \nonumber \\
\ket{\psi}_\mathrm{temporal} &\equiv \alpha\ket{0_t,1_{t+\tau}} + \beta\ket{1_t,0_{t+\tau}},
\end{align}
shown graphically in Fig.~\ref{fig:photonic_qubit_encodings}.

@@

Completely independent of the photon-number degree of freedom, are the spatio-temporal degrees of freedom, which encode the spatial, temporal, or spectral structure of photons. In the temporal domain, for example, we could define the temporal structure of a single photon as,
\begin{align}
\ket\psi_\mathrm{temporal} = \int_{-\infty}^\infty \psi(t) \hat{a}^\dag(t)\,dt\,\ket{0},
\end{align}
where $\hat{a}^\dag(t)$ is the time-specific photonic creation operator, and $\psi(t)$ is the temporal distribution function \cite{bib:RohdeFreqTemp05}. Equivalently, one could take the Fourier transform\index{Fourier transform} of the temporal distribution function and represent the same state in the frequency basis,
\begin{align}
\tilde\psi(\omega) = \mathcal{FT}(\psi(t)).	
\end{align}
Likewise, one could employ a similar representation in the transverse spatial degrees of freedom, with spatial distribution function $\psi(x,y)$.

@@

The TEM modes are discrete, and denoted TEM$_{mn}$, where \mbox{$m,n\in \mathbb{Z}_+$}. TEM modes can be prepared and manipulated using holograms\index{Holograms} in the form of phase-masks\index{Phase-masks}.

### 2018-11-07 Sections/optical_routers.tex
Restructured microwaves

\dropcap{P}{erhaps} the most fundamental building block in any network is routers, devices which switch data packets between multiple inputs and outputs so as to relay them to a destination. Indeed, in many real-world networks, many nodes will purely implement routing, and nothing more elaborate such as computations or other end-user protocols, to be discussed in Sec.~\ref{sec:protocols_quant_int}.

>>>>

\dropcap{P}{erhaps} the most fundamental building block in any network is routers, devices which switch data packets between multiple inputs and outputs so as to relay them to a destination. Indeed, in many real-world networks, many nodes will purely implement routing, and nothing more elaborate such as computations or other end-user protocols, to be discussed in Part~\ref{part:protocols}.

### 2018-11-07 Sections/physical_architectures_for_quantum_computing.tex
Restructured microwaves

@@

\subsubsection{Microwave qubits}\index{Microwave qubits}

To build a scalable quantum computer, multiple qubits are required, with the ability to interact with one another. Hence, it is essential to find ways to transfer quantum information between distinct superconducting qubits. When doing so, it is essential that quantum coherence be preserved. This implies we need to find a different kind of qubit, which can carry information from one place to another, but interacts only weakly with the other qubits and the environment. Photons are the ideal candidate for this (Sec.~\ref{sec:opt_enc_of_qi}). Photonic qubits for carrying information should have frequencies equal to the energy difference between qubit levels. For a superconducting qubit, the energy difference is very small, hence the frequency of optical qubits is in microwave regime, whose wavelength lies in the range $\sim100\mu$m-1m.

Information transfer between distinct superconducting qubits is achieved using a resonator, which acts as a quantum data bus\index{Quantum data bus}. A simple resonator\index{Resonators} is an LC circuit\index{LC circuit}, which can support only one frequency mode, but a waveguide resonator can support multiple modes. In general, the transmission line circuits used in non-linear quantum electric circuits\index{Non-linear quantum electric circuits} are in the form of coplanar waveguides\index{Waveguides}. These waveguides are engineered to handle a particular set of frequencies, and produce transmission lines with tuneable frequency. Tuneable resonators\index{Tuneable resonators} are very important in quantum optics, and are useful in implementing controllable coupling between different quantum elements, and also in shaping photon wave-packets.

In cavity quantum electrodynamics (QED)\index{Quantum electrodynamics} the interaction of a natural atom with an optical photon in the visible wavelength regime is considered. Similarly, the interaction between quantum non-linear electrical circuits and  microwave photons are investigated in circuit QED. The coupling-strength between a natural atom and visible light photon is fixed, where atoms couple weakly with photons \cite{bib:raimond2001manipulating}. Meanwhile, the coupling-strength between a superconducting qubit and a microwave can be manipulated by engineering the parameters of the qubit and resonator, yielding strong and ultra-strong coupling\index{Strong coupling}\index{Ultra-strong coupling} between qubits and photons \cite{bib:wallraff2004strong} (see Fig.~\ref{fig:microwave_qubits}). Furthermore, the coupling between an atom and a photon can be tuned dynamically during the course of an experiment. Several quantum optics components such as mirrors, beamsplitters, circulators and switches can also be designed based on quantum electric circuits.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{microwave_qubits}
\caption{Schematic sketch of the interaction between superconducting qubits and microwave qubits. The superconducting qubits are in the entangled state \mbox{$\frac{1}{\sqrt{2}}(\ket{e,g} + \ket{g,e})$}, where $\ket{g}$ and $\ket{e}$ are the ground and excited states of the superconducting qubits. These are subjected to interact with the flying qubits, the microwave qubit (red dashed arrow). The photons become entangled and the output state of the photons are \mbox{$\frac{1}{\sqrt{2}}(\ket{H,V} + \ket{V,H})$}, where $\ket{H}$ and $\ket{V}$ are the horizontal and vertical polarisation modes respectively.}\label{fig:microwave_qubits}\index{Microwave qubits}
\end{figure}

@@

\subsubsection{Quantum transducers}\index{Quantum transducers}

Due to scalability requirements, superconducting qubits are the most widely used qubit implementation used today. The energy-level spacing in superconducting qubits lie in the microwave regime. Hence to control and transfer information from a superconducting qubit one might need to use microwave photons. In principle, we can use microwave photons to transfer information from one node to another, but such a transmission process is extremely lossy. Also, such processes have very demanding technical requirements, like the design of specialised Niobium waveguides\index{Niobium waveguides}, maintained at extremely low temperatures. Hence it isn't feasible to use microwave photons for the long-distance transfer of quantum information. Meanwhile, it is well known that photons in the visible spectrum can be transmitted easily using optical fibres, with favourable efficiency.

To convert microwave photons to optical photons we can use a quantum transducer. A sketch of a typical design for a quantum transducer\index{Quantum transducers} is shown in Fig.~\ref{fig:quantum_transducer} through a flowchart diagram. The quantum computer is made up of superconducting qubits, which feed quantum information to microwave qubits. The microwave qubits are then interfaced to optical qubits in the visible spectrum through a 3-level quantum system\index{3-level systems}, which can couple at both microwave and optical frequencies. These steps should be reversible. Hence it should be possible to convert the optical qubits back into microwave qubits at the receiving end.

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=\textwidth]{quantum_transducer}
\else
\includegraphics[clip=true, width=0.475\textwidth]{quantum_transducer}
\fi
\caption{Block diagram for the quantum transducer. The quantum computer comprising superconducting qubits couples with the microwave qubit. The microwave qubit and the photonic qubit are coupled by a three-level system in which the energy difference between the levels correspond to both microwave and visible optical frequencies. The thick arrows denote the forward process, required to convert the microwave to optical frequencies, and the dashed arrows represent the reverse process, required at the receiving end to convert the optical frequency to a microwave frequency.}\label{fig:quantum_transducer}
\end{figure}

There are several proposals for quantum transducers in existence and they can be classified into two major classes:
\begin{itemize}
	\item Opto-mechanical \cite{bib:rabl2010quantum, bib:barzanjeh2011entangling, bib:bochmann2013nanomechanical, bib:didier2014quantum, bib:schuetz2015universal, bib:shumeiko2016quantum, bib:stannigel2010optomechanical}.
	\item Spin-ensembles \cite{bib:imamouglu2009cavity, bib:blum2015interfacing}.
\end{itemize}

The opto-mechanical quantum transducer\index{Opto-mechanical quantum transducer} (see Fig.~\ref{fig:opto_mechanics_transducer}), as the name suggests, combines optical components with a nano-mechanical resonator and converts the microwave photon\index{Phonons} into a phonon (acoustic) mode. The acoustic mode is then transmitted via waveguides\index{Waveguides}. Since we need to fabricate waveguides with very high precision to transmit phonon modes, this scheme is not suitable for communicating between two distant quantum computers. A coupling of the phonon mode to the optical photon mode in the visible region was suggested to enable long-distance transfer of quantum information.

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=\textwidth]{transducer_scheme_1}
\else
\includegraphics[clip=true, width=0.475\textwidth]{transducer_scheme_1}
\fi
\caption{Scheme for an opto-mechanics-based quantum transducer. There are two possible ways of converting microwaves. The final steps for the process in which acoustic modes are transported using waveguides is enclosed by a brown coloured box with dashed outlines labeled (a). Similarly the blue coloured box labeled (b) represents the scheme where phonons are converted to optical photons which are then transmitted via optical fibres. The initial few steps consisting of the superconducting qubit, transmission line resonator and microwaves are common to both processes.}\label{fig:opto_mechanics_transducer}\index{Opto-mechanical quantum transducer}
\end{figure}

The Hamiltonian of an opto-mechanical quantum transducer, which converts a microwave photon to optical photon using an intermediate nano-mechanical resonator\index{Nano-mechanical resonator} reads,
\begin{align}
\hat{H} &= \hbar \omega_{1} \, \hat{a}_{1}^{\dag} \hat{a}_{1} + \hbar \omega_{2} \, \hat{a}_{2}^{\dag} \hat{a}_{2} \nonumber\\
&+ \hbar \Omega \, \hat{b}^{\dag} \hat{b} + \hbar \, g \, (\hat{b}+\hat{b}^{\dag}) (\hat{a}_{2}^{\dag} \hat{a}_{1} + \hat{a}_{1}^{\dag} \hat{a}_{2}),
\end{align}
where $\omega_{1}$ ($\omega_{2}$) is the frequency of the microwave (optical) photon, and $\Omega$ is phonon frequency. The operators $\hat{a}_{1}$ ($\hat{a}_{1}^{\dag}$) and $\hat{a}_{2}$ ($\hat{a}_{2}^{\dag}$) denote the annihilation (creation) operators corresponding to the microwave and optical photons respectively. Meanwhile, $\hat{b}^{\dag}$ ($\hat{b}$) denotes the phonon creation (annihilation) operator corresponding to the phonons. The factor $g$ is the coupling-strength between the microwave, phonon and photon modes. This design for a quantum transducer is widely preferred, since the optical photons in the visible spectrum can be transmitted over long distances using fibre optics. But the scheme requires two intermediate conversions, each of which reduces overall efficiency.

The spin-ensemble-based quantum transducer\index{Spin-ensemble quantum transducer} (see Fig.~\ref{fig:spin_ens_transducer}) is an alternative to the opto-mechanical quantum transducer. In this scheme an ensemble of spins interact with microwave qubits via magnetic dipole coupling\index{Magnetic dipole coupling}, while the superconducting qubits interact via electric dipole coupling\index{Electric dipole coupling} with the microwave coupling. The Hamiltonian for such a system is,
\begin{align}
\hat{H} = \hat{H}_{\mathrm{mw}} + \hat{H}_{\mathrm{spin}} + \hat{H}_{\mathrm{opt}},
\end{align}
where,
\begin{align}
\hat{H}_{\mathrm{mw}} &= \hbar \omega_\mathrm{sq} \hat\sigma_\mathrm{sq}^{\dag} \hat\sigma_\mathrm{sq} + \hbar \omega_{\mu} \hat{a}^{\dag} \hat{a} + \hbar g_{\mu} (\hat{a}^{\dag} \hat\sigma_\mathrm{sq} + \hat{a} \hat\sigma_\mathrm{sq}^{\dag}),\nonumber \\
\hat{H}_{\mathrm{spin}} &= \hbar g_\mathrm{s} (\hat\sigma_\mathrm{ba}^{\dag} \hat\sigma_\mathrm{ba} + \hat\sigma_\mathrm{bs}^{\dag} \hat\sigma_\mathrm{bs}), \nonumber\\
\hat{H}_{\mathrm{opt}} &= \hbar g_\mathrm{ab} (\hat\sigma_\mathrm{ba}^{\dag} \hat{c} + \hat{c}^{\dag} \hat\sigma_\mathrm{ba}).
\end{align}

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.9\textwidth]{transducer_scheme_2}
\else
\includegraphics[clip=true, width=0.475\textwidth]{transducer_scheme_2}
\fi
\caption{The spin-ensemble-based quantum transducer. Microwave photons are converted to optical photons via a spin-ensemble.}\label{fig:spin_ens_transducer}\index{Spin-ensemble quantum transducer}
\end{figure}

The factor $\omega_\mathrm{sq}$ is the frequency of the superconducting qubit, and $\hat\sigma_\mathrm{sq}^{\dag}$ and $\hat\sigma_\mathrm{sq}$ are the raising and lowering operators\index{Raising operators}\index{Lowering operators} corresponding to the superconducting qubits. The frequency of the microwaves is given by $\omega_{\mu}$, and the $\hat{a}^{\dag}$ and $\hat{a}$ are the creation and annihilation operators for the microwave photons. The factor $g_{s}$ is the coupling strength between the various levels of the spin, and $\hat\sigma_\mathrm{ba}$ and $\hat\sigma_\mathrm{bs}$ are the spin operators corresponding to the transition between the level $a$, $b$ and $s$. Finally, the coupling strength of the spin interaction with the photon is denoted by $g_\mathrm{ab}$, and $\hat{c}^{\dag}$ ($\hat{c}$) is the creation (annihilation) operator corresponding for the photon. Again this is a two-step process, which is in addition beset with the problem of inhomogenous line broadening\index{Inhomogenous line broadening}. The design of an experimental, high-fidelity quantum transducer is still an open and ongoing challenge in the field of quantum technology.

>>>>

%
% Atomic Ensembles
%

\subsection{Atomic ensembles}

\comment{To do}

@@

@@
